Home Nighttime Cough Monitoring

### 2025-02-11 Lilah Melzer/cough_monitor_analysis.qmd
cough monitor surveys at first visit

```{r}
# See SAS scoring instructions (from Quitter's CFQ-R website).docx for
# instructions

@@

    sid, cfqr_caregivers_613_timestamp, cfq_r_p_1:cfq_r_p_44

@@

  select(sid, Date, physical:weight)

@@

    sid, cfqr_children_ages_611_timestamp, cfq_r_y_1:cfq_r_y_35

@@

  select(sid, Date, physical:digest)

@@

    sid, cfqr_adolescents_and_adults_14_years_timestamp, cfq_r_a_1:cfq_r_a_50

@@

  select(sid, Date, physical:digest)
# Write for checking
write.csv(df %>%

@@

    sid, cfqr_caregivers_613_timestamp, cfq_r_p_1:cfq_r_p_44
  ), file = "~/cfqr_parent_6_13.csv", na = "", row.names = F)
write.csv(df %>%
    sid, cfqr_children_ages_611_timestamp, cfq_r_y_1:cfq_r_y_35
  ), file = "~/cfqr_children_6_11.csv", na = "", row.names = F)
write.csv(df %>%
    sid, cfqr_adolescents_and_adults_14_years_timestamp, cfq_r_a_1:cfq_r_a_50
  ), file = "~/cfqr_teens_adults.csv", na = "", row.names = F)

@@

>>>>

```{r}
# See SAS scoring instructions (from Quitter's CFQ-R website).docx for
# instructions
df <- df %>%
  fill(c(date_v1_cf, date_v1_hc)) %>%

@@

    sid, date_v1_cf, date_v1_hc,
    cfqr_caregivers_613_timestamp, cfq_r_p_1:cfq_r_p_44

@@

    Date = coalesce(Date, date_v1_cf),
    Date = coalesce(Date, date_v1_hc),
    Survey = "CFQ-R Caregivers 6-13"
    sid, Survey, Date, physical:weight
  filter(!if_all(physical:weight, ~ is.na(.)))

@@

    sid, date_v1_cf, date_v1_hc,
    cfqr_children_ages_611_timestamp, cfq_r_y_1:cfq_r_y_35

@@

    Date = coalesce(Date, date_v1_cf),
    Date = coalesce(Date, date_v1_hc),
    Survey = "CFQ-R Children Ages 6-11"
    sid, Survey, Date, physical:digest
  filter(!if_all(physical:digest, ~ is.na(.)))

@@

    sid, date_v1_cf, date_v1_hc,
    cfqr_adolescents_and_adults_14_years_timestamp, cfq_r_a_1:cfq_r_a_50

@@

    Date = coalesce(Date, date_v1_cf),
    Date = coalesce(Date, date_v1_hc),
    Survey = "CFQ-R Adolescents and Adults 14 Years"

@@

    sid, Survey, Date, physical:digest
  filter(!if_all(physical:digest, ~ is.na(.)))
# Combine
surveys <- full_join(cfqr_parent_6_13, cfqr_children_6_11)
surveys <- full_join(surveys, cfqr_teens_adults)

@@

## Correlation between baseline surveys and coughs

```{r}
```
